A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828

### 2018-09-09 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
#knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
# knitr::opts_chunk$set(dev = "Cairo")
#knitr::opts_chunk$set(dev = "CairoPDF")
knitr::opts_chunk$set(dev = "CairoPS")
# knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")
knitr::opts_chunk$set(fig.width=13.5,fig.height=8)

>>>>

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "figures_HistoricalMethods2018/", dpi = 300)
knitr::opts_chunk$set(dev = "CairoPS")
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")
knitr::opts_chunk$set(fig.width=13.5,fig.height=8)
